Linear stability analysis for \textit{monami} in a submerged sea grass bed

### 2015-10-26 Paper_JFM/Response/Response.tex

\textit{  Fig 2 $\& 3$:
In both captions a value for the eddy viscosity is given. Was there any physical basis for this value? If not, how was it chosen? And how critical are the comparisons between theory and experiment to its value?
}

The constant eddy viscosity of 0.1 Pa s is chosen based on eddy viscosity profile shown in Figure 5 for lab scale experiments of Ghisalberti and Nepf (2004). As the referee realized, the exact value of the eddy viscosity varies with depth in the water column. But overall, the eddy viscosity arises from the eddies the vegetation generates. The scale of velocity for these eddies is the free stream speed ($U \sim 0.1$ m/s), and the size of the eddies is the width of the grass blade ($d \sim 0.01$ m). According to Ghisalberti and Nepf (2004), the eddy viscosity is approximately $\mu \approx 0.1 \rho U d = 0.1$ Pa s). The Reynolds number $\Rey$ is the only parameter that depends on the eddy viscosity. Any uncertainty in the eddy viscosity translates into an uncertainty in the critical Reynolds number for the onset of the instability. {\bf Any changes to the manuscript.}
% (The limited growth of vegetated shear layers. \textit{Water Resources Research 40 (7), 2004} )

We have now revised the manuscript to include this discussion. The manuscript now reads:

\textbf{
The measured values of eddy viscosity vary with depth in the water column \citep{Nepf04}; we use $\mu= 0.1$ Pa s as a representative value from this range for comparison with experiments.
}

and we have removed the statement of the value of eddy viscosity from the captions of figures 2 and 3.

@@

\end{enumerate}

\newpage
\centerline{\textbf{Matched asymptotic solution}}

Here we present an asymptotic solution of equation (3.1) for $N_g \gg 1$, which should be helpful in clarifying many questions the referee has related to the boundary layer near the grass top. For simplicity of calculation in this particular calculation we assume the grass to extend from $y=0$ to $y=H$, i. e. a submergence ratio is 0.5. 
Using $ U_0 = (-dP/dx)H^2/\mu$ as velocity scale, $H$ as length scale, we rescale velocity as $U= U_0 \bar{U}$ and $y = H \bar{y}$. Equation (3.1) is then transformed to  
\begin{equation}
\begin{split}
 \bar{U}_{\bar{y}\bar{y}}+1 - \frac{\rho U_0 H}{\mu} C_N d N_g \bar{U}^2 =0, \quad &\text{ for } y<0\\
 \bar{U}_{\bar{y}\bar{y}}+1 - R \Ndg \bar{U}^2=0, \quad &\text{ for } y>0.
\end{split}
\end{equation}
For notational convenience, we will drop the overbar and define a drag parameter as $D_g = R\Ndg$ for $-1<y\le 0$, $D_g = 0$ for $0<y\le 1$, grass top is at $y=0$ and the bottom surface is at $y=-1$. Equation (3.1) now reads
\begin{equation}
\begin{split}
 {U}_{{y}{y}}+1 - D_g{U}^2 &=0.
\end{split}
\end{equation}
We use the zero shear boundary condition on both the boundaries ($y=-1,1$) as mentioned in the manuscript.

\vspace{2mm}
\noindent
\textbf{Asymptotic Solution of 3.1 below the grass}

\noindent
We observe that $U = \sqrt{(1/D_g)}$ is a stationary point of above equation, where both $U_{yy}=0$ and $U_y =0 $. By multiplying with $U_y$ and integrating once, we get
\begin{equation}
\begin{split}
 \frac{1}{2} \left( \frac{dU}{dy} \right)^2 +U - \frac{1}{3} D_g U^3 + C = 0
\end{split}
\label{eqn:above}
\end{equation}
Where C is a constant of integration, which can be determined by observing that as $U$ approaches $1/\sqrt{D_g}$, $U_y$ approaches zero. Applying this condition gives $C = -\dfrac{2}{3\sqrt{D_g}}$. Using the value of $C$, \eqref{eqn:above} becomes 
\begin{equation}
\begin{split}
 \frac{dU}{dy} = \sqrt{\frac{2}{3}D_g U^3+\frac{4}{3\sqrt{D_g}}-2U }
\end{split}
\end{equation}
We further use the substitution $U=\dfrac{1}{\sqrt{D_g}} u $ in the above equation, which simplifies it to
\begin{equation}
\begin{split}
%  \frac{1}{\sqrt{D_g}}\frac{du}{dy} &= \frac{1}{D_g^{1/4}}\sqrt{\frac{2}{3}} \sqrt{ u^3+2-3u } \\
%  \frac{du}{dy} &= {D_g^{1/4}}\sqrt{\frac{2}{3}} \sqrt{ u^3+2-3u } \\
 \frac{du}{(u-1)\sqrt{u+2} } &= {D_g^{1/4}}\sqrt{\frac{2}{3}} dy
\end{split}
\end{equation}
Above equation can be integrated to obtain the solution in the vegetated region as
\begin{equation}
\begin{split}
u &= 3 \coth \left(\frac{C_1-y D_g^{1/4}}{\sqrt{2}}  \right)^2-2 \\
U &= \frac{1}{\sqrt{D_g}} \left( 3 \coth^2 \left(\frac{C_1-y D_g^{1/4}}{\sqrt{2}}  \right)-2    \right)
\label{under_grass_sol}
\end{split}
 \hspace{1cm} \text{for $-1\le y\le 0$,}
\end{equation}
where $C_1$ is constant of integration, which can be found by matching the shear stress applied by the flow above the grass at the tip of the grass.

\vspace{2mm}
\noindent
\textbf{Solution above the grass}

\noindent
Above the grass, the dimensionless form of equation (3.1) translates to
\begin{equation}
 U_{yy}+1=0
\end{equation}
which can be integrated together with the zero shear boundary condition at top to provided
\begin{equation}
 U(y) = y-y^2/2+C_2 \hspace{1cm} \text{for $0<y<1$}
 \label{above_grass_sol}
\end{equation}
Where $C_2$ is constant of integration.

\vspace{2mm}
\noindent
\textbf{Matching the solution obtained by \eqref{under_grass_sol} and \eqref{above_grass_sol} }

\noindent
The value of $C_1$ and $C_2$ can be determined by matching the solution \eqref{under_grass_sol} and \eqref{above_grass_sol} at the grass tip.
Matching the shear stress at the grass top results in
\begin{equation}
\frac{3\sqrt{2}}{D_g^{1/4}} \coth\left(\dfrac{C_1}{\sqrt{2}}\right) \csch^2\left(\dfrac{C_1}{\sqrt{2}}\right) = 1;
\label{C1_eq}
\end{equation}
Above equation can be solved numerically, but here we will solve it asymptotically for $D_g \gg 1$. We expect $C_1 \ll 1$ in this limit, and the terms in \eqref{C1_eq} may be expanded in this limit to get
\begin{equation}
\begin{split}
\frac{3\sqrt{2}}{D_g^{1/4}} \left( \frac{\sqrt{2}}{C_1} \right) \left( \frac{2}{C_1^2} \right) &= 1 \\
C_1 = \frac{(12)^{1/3}}{D_g^{1/12}}
\end{split}
\end{equation}
The boundary layer length scale may be derived from examining the scale of $y$ for which the argument of \eqref{under_grass_sol} changes asymptotic order. This examination implies $C_1 \sim O(y D_g^{1/4})$ or $y = O(D_g^{-1/3})$. The scale for velocity in the boundary layer is the value of \eqref{under_grass_sol} at $y=0$.
\begin{align}
 U_\text{top} &=  \frac{1}{\sqrt{D_g}} \left( 3 \coth^2 \left(\frac{C_1}{\sqrt{2}}  \right)-2    \right) \\
              &\approx  \frac{1}{\sqrt{D_g}} \left( \frac{6}{C_1^2} -2    \right) \\
              &\approx \frac{1}{\sqrt{D_g}} \frac{6D_g^{1/6}}{12^{2/3}} \\
              &\approx \left( \dfrac{3}{2} \right)^{1/3} D_g^{-1/3}.
\end{align}

% 
% 
% Through constant $C_1$ a natural length scale $\delta$ arises when $\delta D_g^{1/4}$ balances $C_1$ in equation \eqref{under_grass_sol}, which gives $\delta \sim D_g^{-1/3}$ or $\delta \sim (R\Ndg)^{-1/3}$. We can also obtain scale of velocity in the boundary layer by substituting $y=0$ in the \eqref{under_grass_sol} and using asymptotic expansion of $\coth(x)$, doing this expansion leads to 
% \begin{equation}
% \begin{split}
% U(y)-U_{tip} &\sim \frac{1}{\sqrt{D_g}}\frac{1}{C_1^2}\\
% U(y)-U_{tip} &\sim D_g^{-1/3}\\
% U(y)-U_{tip} &\sim (R\Ndg)^{-1/3}
% \end{split}
% \end{equation}
% near the grass tip. 
We have employed one of the many possible methods to understand the structure of the solution of (3.1); other methods can also be used to reach the same conclusions.
In th manuscript we have presented the outline of an essentially identical method.
For a general treatment of the topic, we refer the referee to the book by \cite{Hinch1991}. % (Perturbation Methods by E.J. Hinch, Cambridge Texts in Applied Mathematics ).

\newpage
\bibliography{Grass}{}
\bibliographystyle{jfm}
% 
% \newpage
% \textbf{ About the Origin of boundary layer $\delta$}
% 
% \centerline{Ravi's new edits}
% 
% In order to match shear stress at the grass tip applied by the fluid above the grass, the flow with in the grass increases from an approximately constant velocity $U_g = \sqrt{\frac{-dp/dx}{\rho C_N d N_g}}$ in a region $\delta$ to a value so that both velocity and shear stress are continuous across the grass tip. Again for in-depth discussion about such problem can be found in the book of Hinch.   
% 
% \textbf{About the estimated value of $H/\delta$ from Figure-1}
% 
% I think reviewer have understood the case-I mentioned for Figure-1 as the one from 2002 paper ( Mixing layer and coherent structures in vegetated aquatic flows, \textit{J. Geophys. Res. 107} ), whereas we are referring to the case-I from the 2004 paper ( The limited growth of vegetated shear layers, \textit{Water Resource Research 40(7)} ). In this case the channel width is $41cm$, implying $H=20.5 cm$ hence $H/\delta=4.02$. We would also like to point out that we have used log scale on y-axis in Figure-2, and indeed $H/\delta \approx 5$ for all the experimental observation shown in Figure-2.
% 
% \textbf{Basis for eddy viscosity}
% 
% The constant eddy viscosity of 0.1 Pa s is chosen based on eddy viscosity profile shown in Figure-5 for lab scale experiments of Ghisalberti and Nepf (The limited growth of vegetated shear layers. \textit{Water Resources Research 40 (7), 2004} )
